---
title: 'umart generates umap art'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- badges: start -->

[![CRAN_Status_Badge](https://r-pkg.org/badges/version/umart)](https://cran.r-project.org/package=umart)
[![CRAN\_Release\_Badge](https://www.r-pkg.org/badges/version-ago/umart)](https://CRAN.R-project.org/package=umart) 
[![Codecov test coverage](https://codecov.io/gh/Nelson-Gon/umart/branch/main/graph/badge.svg)](https://codecov.io/gh/Nelson-Gon/umart?branch=main)
[![R-CMD-check](https://github.com/Nelson-Gon/umart/actions/workflows/devel-check.yaml/badge.svg)](https://github.com/Nelson-Gon/umart/actions/workflows/devel-check.yaml)
![test-coverage](https://github.com/Nelson-Gon/umart/workflows/test-coverage/badge.svg)
[![Project Status](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/) 
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![GitHub last commit](https://img.shields.io/github/last-commit/Nelson-Gon/umart.svg)](https://github.com/Nelson-Gon/umart/commits/main)
[![GitHub issues](https://img.shields.io/github/issues/Nelson-Gon/umart.svg)](https://GitHub.com/Nelson-Gon/umart/issues/)
[![GitHub issues-closed](https://img.shields.io/github/issues-closed/Nelson-Gon/umart.svg)](https://GitHub.com/Nelson-Gon/umart/issues?q=is%3Aissue+is%3Aclosed)
[![PRs Welcome](https://img.shields.io/badge/PRs-welcome-brightgreen.svg?style=flat-square)](https://makeapullrequest.com)
[![Maintenance](https://img.shields.io/badge/Maintained%3F-yes-green.svg)](https://GitHub.com/Nelson-Gon/umart/graphs/commit-activity)
<!-- badges: end -->

# Installation 


```{r install, eval=FALSE}
devtools::install_github("Nelson-Gon/umart")
```


# Load library 

```{r lib_call}
library(umart)

```


# Data Generation 

```{r generate_data}
r_x <- generate_data(mean = 20.5, sd = 0.2)
r_y <- generate_data(mean = 10.5, sd = 0.1)
df <- data.frame(x = r_x, y=r_y, group = rep(paste0("grp_", 1:5), 10))
```


# Run UMAP 

```{r run_umap}
umap_df <- run_umap(df[, -3],neighbors = 5,  seed = 520)
```

# Generate umart 


```{r generate_art}
generate_umart(umap_df, group_col = df$group,
               bg_color = "#f2f5f3", use_geom = "geom_segment",
               xend = 0.5, yend = 12)
```

# Many neighbors 

```{r}
umaps <- run_umap(df[, -3],neighbors = 2:5, seed = 20)
groups <- rep(paste0("g_", 1:5), 40)

generate_umart(umaps, group_col = groups, opacity = 0.15,
               bg_color = "#f6feff", use_geom = "geom_col",
               use_palette = "Blues"
               ) 


```

---


Please note that the `umart` project is released with a [Contributor Code of Conduct](https://github.com/Nelson-Gon/umart/blob/main/.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

For further exploration, please `browseVignettes("umart")`.

To raise an issue, please do so
[here](https://github.com/Nelson-Gon/umart/issues)

Thank you, feedback is always welcome :)
